SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2019-04-02 design_arch.tex
Reworded last two paragraphs.

\noindent \textbf{Feature Selection:} Perceptrons essentially
integrate contributions from different features to get a single sum
representing the final confidence.  Thus, perceptron learning can only
be as good as the set of features chosen.  Interestingly, this is what
makes perceptron learning scalable, as it can easily learn to
incorporate newer information in the form of new features.  Some of
the features we developed use information derived directly from
program execution, agnostic to the {\color{red}underlying} prefetcher.  Beyond that,
the feature set can be expanded to convey any useful information or
metadata available in the {\color{red}underlying} prefetcher.

\noindent \textbf{Using Metadata from the Prefetcher:} Some of the 
internal counters specific to the underlying prefetcher can be suitable candidates
for the perceptron features. To make sure that the perceptron layer sees that, 
the relevant meta-data must be exported from the prefetcher to PPF. This way,
PPF can be optimized to work tightly-knit with the {\color{red}underlying} prefetcher.

>>>>

\noindent \textbf{Feature Selection:} Perceptrons essentially
integrate contributions from different features to get a single sum
representing the final confidence.  Thus, perceptron learning can only
be as good as the set of features chosen.  Interestingly, this is what
makes perceptron learning scalable, as it can easily learn to
incorporate newer information in the form of new features.  Some of
the features we developed use information derived directly from
program execution, agnostic to the {\color{red}underlying} prefetcher.  Beyond that,
the feature set can be expanded to convey any useful information or
metadata available in the {\color{red}underlying} prefetcher itself.

\noindent \textbf{Using Metadata from the Prefetcher:} Some of the 
internal counters specific to the underlying prefetcher can be suitable candidates
for perceptron features. Therefore, all relevant meta-data must be exported from 
the prefetcher to PPF. In this way, PPF can be optimized to work in a tight-knit fashion
with the {\color{red}underlying} prefetcher.
